### 2017-11-28 monograph/thesis/chapters/good_practices.tex
Created some weblink references/footnotes.
Added some missing TODO statements and creates lists for loose URLs

@@

    \url{https://help.github.com/articles/configuring-a-remote-for-a-fork/}

    \url{https://stackoverflow.com/questions/2739376/definition-of-downstream-and-upstream}

@@

@@

    \citeonline{trackingChanges},

    \subsection{Test Driven Development}

    \footnote{\url{https://blog.codinghorror.com/check-in-early-check-in-often/}}

    \cite{aspectOriented}

@@

    \url{http://rhodesmill.org/brandon/2012/one-sentence-per-line/}
    \url{https://www.google.com.br/search?q=semantic+linefeeds}
    \url{https://news.ycombinator.com/item?id=4642395}
    \url{https://en.wikipedia.org/wiki/Wikipedia:Don%27t_use_line_breaks}
    \url{https://erambler.co.uk/blog/semantic-linefeeds/}
    \url{https://vi.stackexchange.com/questions/9828/insert-a-newline-after-punctuations}
    \url{https://blog.doismellburning.co.uk/semantic-linebreaks/}
    \url{https://scott.mn/2014/02/21/semantic_linewrapping/}
    \url{https://stackoverflow.com/questions/899114/when-you-write-tex-source-how-do-you-use-your-editors-word-wrap}

>>>>

    \begin{enumerate}[leftmargin=*]
        \item \url{https://github.com/k88hudson/git-flight-rules}
        \item \url{https://github.com/i0natan/nodebestpractices}
    \end{enumerate}

@@

    \begin{enumerate}[leftmargin=*]
        \item \url{https://help.github.com/articles/configuring-a-remote-for-a-fork/}
        \item \url{https://stackoverflow.com/questions/2739376/definition-of-downstream-and-upstream}
    \end{enumerate}

@@

    TODO

@@

    \begin{enumerate}[leftmargin=*]
        \item \citeonline{trackingChanges},
        \item \footnote{\url{https://blog.codinghorror.com/check-in-early-check-in-often/}}
        \item \cite{aspectOriented}
    \end{enumerate}

@@

    \begin{enumerate}[leftmargin=*]
        \item \url{http://rhodesmill.org/brandon/2012/one-sentence-per-line/}
        \item \url{https://www.google.com.br/search?q=semantic+linefeeds}
        \item \url{https://news.ycombinator.com/item?id=4642395}
        \item \url{https://en.wikipedia.org/wiki/Wikipedia:Don%27t_use_line_breaks}
        \item \url{https://erambler.co.uk/blog/semantic-linefeeds/}
        \item \url{https://vi.stackexchange.com/questions/9828/insert-a-newline-after-punctuations}
        \item \url{https://blog.doismellburning.co.uk/semantic-linebreaks/}
        \item \url{https://scott.mn/2014/02/21/semantic_linewrapping/}
        \item \url{https://stackoverflow.com/questions/899114/when-you-write-tex-source-how-do-you-use-your-editors-word-wrap}
    \end{enumerate}
